First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-12-04 MY_PUBLICATIONS/PRL/draft_v1/body.tex
updated

the original proposal\cite{e12_10_003_proposal}, we conclude that the results presented on this Letter (although very interesting) do not have the
necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.

%We conclude that these results although very interesting, does not have the sufficient statistics and the
%required number of high missing momentum settings to make a definitive argument about the underlying physics observed.\\

%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs

>>>>

the original proposal\cite{e12_10_003_proposal}, we conclude that additional beam time is required to measure the full kinematic coverage as the results presented on this Letter
(although very interesting) do not have the necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed. \\
\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.

### 2019-12-04 MY_PUBLICATIONS/PRL/draft_v1/introduction.tex
updated

Being the only bound two-nucleon system, the deuteron serves as a starting point to study the strong nuclear force at the subfermi level which is currently

@@

Short-range studies of the deuteron are also important in determining whether or to what extent is the description of nuclei in terms of nucleon/meson degrees of freedom valid before
having to include explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
which a transition between nucleonic to quark degrees of freedom been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
This Letter presents first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleonic degrees of freedom is expected.\\

@@

electro-disintegration reaction at very high neutron recoil (or missing) momenta and within the PWIA kinematics. In this approximation, the virtual photon couples to
the proton which is ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$. This gives direct access to the deuteron momentum distributions since the scattered neutron momentum remains unchanged from its initial state. \\

@@

up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs played a significant role and their inclusion was necessary in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214}

@@

The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, due to statistical limitations it was impossible to select kinematical bins in $\theta_{nq}$ where

@@

the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) versus $\theta_{nq}$ presented verified the strong anisotropy of FSIs with recoil angle also observed in Hall B\cite{PhysRevLett.98.262502}. Most importantly, for recoil

>>>>

Being the only two-nucleon bound system, the deuteron serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently

@@

Short-range studies of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom is still valid before
having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
which a transition between nucleonic to quark degrees of freedom been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.\\

@@

electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA the virtual photon couples to
the proton which is subsequently ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.

@@

up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs played a significant role and had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214}

@@

The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it impossible to select kinematical bins in $\theta_{nq}$ where

@@

the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented verified the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}. Most importantly, for recoil

### 2019-12-04 MY_PUBLICATIONS/PRL/draft_v1/prl.tex
updated

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version xx as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
  neutron recoil momenta up to 1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the neutron recoil
  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and comparison
  to recent theoretical calculations show data to be sensitive to momentum distributions up to $\sim$ 700 MeV/c recoil momenta.

%  momentum distribution has been determined from measured for neutron recoil momenta up to 1.14 GeV/c.

  %An article usually includes an abstract, a concise summary of the work
%covered at length in the main body of the article. It is used for
%secondary publications and for information retrieval purposes.
%For PRL, the rule of thumb is that the abstract should be less than
%8 lines and the text (excluding authors, abstract but including tables,
%figures and references) should be less than 4 pages (leave about 20 lines
%empty on page 4) in two-column format.
%PRL and PRD papers have to have PACS (Phsyics and Astronomy Classification
%Scheme) numbers. Please see {\tt http://www.aip.org/pacs/} for the numbers
%relevant to your paper. A set of standard references can be found at the
%end of this example paper.
\end{abstract}

@@

\input introduction.tex
\input body.tex
%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\   %This space must remain here to keep the acknowledgemn section in place
\input acknowledgement.tex   % input acknowledgement
\bibliography{prl}

\end{document}
%
% ****** End of file template.aps ******

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 01 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

%CURRENTLY CORRECTING
\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ for 
  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c and neutron recoil angles ($\theta_{nq}$) of 35, 45 and 75 degrees are presented. At the selected kinematics,
  Meson Exchange Currents (MEC) and Isobar Configurations (IC) are suppressed. At recoil angles of 35 and 45 degrees, Final State Interactions (FSI) have been suppressed
  and the Plane Wave Impulse Approximation (PWIA) provides the dominant cross section contribution. A comparison to recent theoretical calculations show the data to be sensitive
  to momentum distributions up to $p_{r}\sim$ 750 MeV/c.
\end{abstract}

@@

\input introduction.tex
\input body.tex
\input acknowledgement.tex    % input acknowledgement
\bibliography{prl}
%.\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\end{document}
%
% ****** End of file template.aps ******
